---
title: "AFCP: Average Feature Choice Probability "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{afcp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette illustrates how to estimate average feature choice probabilities using the `afcp` package and the output of the `amce()` function from the package `cjoint`. 

In a binary choice conjoint task, the average feature choice probability between two levels $a$ and $b$ of attribute $l$ or $AFCP_l(a, b)$ captures the share of comparisons in which the profile where attribute $l$ is set to $a$ is selected over another profile in which attribute $l$ is set to $b$.  

```{r setup}
library(cjoint)
library(afcp)
```

We will use the immigration conjoint example built into the `cjoint` package.

```{r}
data("immigrationconjoint")
```

In this design, some cross-attribute restrictions were imposed. Here we will focus on an attribute that was assigned completely at random: `Language Skills`. This attribute has three levels

```{r}
table(immigrationconjoint$`Language Skills`)
```

We start by running the estimator in `cjoint` - as we are focusing on an attribute with no randomization restrictions, we can specify "uniform" randomization.

```{r}
amce_results <- amce(Chosen_Immigrant ~ `Language Skills`, data=immigrationconjoint, cluster=T, respondent.id = "CaseID", design = "uniform")
```

The output of `amce()` is an `amce` object which the `afcp()` function takes as input. For `afcp()`, we also need to specify the names of the columns denoting the task and profile as well as the respondent identifier. By default,
`afcp()` will use the baseline level from the `amce` object, but this can be overriden using the `baseline` argument. 

```{r}
afcp_results <- afcp(amce_results, respondent.id = "CaseID", task.id = "contest_no", profile.id = "profile", attribute = "Language Skills")
```

`afcp()` returns a list with three dataframes. The first, `afcp`, contains the estimated AFCPs for each attribute level relative to the specified baseline as well as z-statistics and p-values for the hypothesis test of the null that the AFCP is equivalent to $0.5$.

```{r}
afcp_results$afcp
```

The second data frame, `wald`, contains the wald test statistics and p-values for the hypothesis test of the restriction that the direct ($AFCP_l(a,b) - .5$) and indirect ($AFCP_l(a,c) - AFCP_l(b,c)$) preference measures are equivalent for all other levels $c$ in the attribute.

```{r}
afcp_results$wald
```

The third data frame, `direct_indirect` contains the estimated direct ($AFCP_l(a,b) - .5$) and indirect ($AFCP_l(a,c) - AFCP_l(b,c)$) preference measures for each other attribute level $c$.

```{r}
afcp_results$direct_indirect
```

