---
title: "AFCP: Average Feature Choice Probability"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AFCP: Average Feature Choice Probability}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette illustrates how to estimate average feature choice probabilities using the `afcp` package and the output of the `amce()` function from the package `cjoint`. 

In a binary choice conjoint task, the average feature choice probability between two levels $a$ and $b$ of attribute $l$ or $AFCP_l(a, b)$ captures the share of comparisons in which the profile where attribute $l$ is set to $a$ is selected over another profile in which attribute $l$ is set to $b$.  

```{r setup}
library(cjoint)
library(afcp)
```

We will use the immigration conjoint example built into the `cjoint` package in which U.S. respondents were presented with pairs of immigrant profiles and asked which individual they believe should be admitted into the United States.

```{r}
data("immigrationconjoint")
```

In this design, some cross-attribute restrictions were imposed. Here we will focus on an attribute that was assigned completely at random: `Language Skills`. This attribute has four levels

```{r}
table(immigrationconjoint$`Language Skills`)
```

We start by running the estimator in `cjoint` - as we are focusing on an attribute with no randomization restrictions, we can specify "uniform" randomization.

```{r}
amce_results <- amce(Chosen_Immigrant ~ `Language Skills`, data=immigrationconjoint, cluster=T, respondent.id = "CaseID", design = "uniform")
summary(amce_results)
```

The output of `amce()` is an `amce` object which the `afcp()` function takes as input. For `afcp()`, we also need to specify the names of the columns denoting the task and profile as well as the respondent identifier. By default,
`afcp()` will use the baseline level from the `amce` object, but this can be overriden using the `baseline` argument. 

```{r}
afcp_results <- afcp(amce_results, respondent.id = "CaseID", task.id = "contest_no", profile.id = "profile", attribute = "Language Skills")
```

`afcp()` returns a list with three dataframes. The first, `afcp`, contains the estimated AFCPs for each attribute level relative to the specified baseline as well as z-statistics and p-values for the hypothesis test of the null that the AFCP is equivalent to $0.5$.

```{r}
afcp_results$afcp
```

The second data frame, `wald`, contains the wald test statistics and p-values for the hypothesis test of the restriction that the direct ($AFCP_l(a,b) - .5$) and indirect ($AFCP_l(a,c) - AFCP_l(b,c)$) preference measures are equivalent for all other levels $c$ in the attribute.

```{r}
afcp_results$wald
```

The third data frame, `direct_indirect` contains the estimated direct ($AFCP_l(a,b) - .5$) and indirect ($AFCP_l(a,c) - AFCP_l(b,c)$) preference measures for each other attribute level $c$.

```{r}
afcp_results$direct_indirect
```

Here we have some evidence of a divergence between direct and indirect preferences. Respondents strongly prefer, in pairwise comparisons, an immigrant who speaks fluent English over one who speaks broken English. However, they appear to prefer an immigrant who speaks broken English to one who speaks through an interpreter at about the same level as they prefer an immigrant who speaks fluent English to one who speaks through an interpreter.

